\documentclass[a4paper,10pt]{article}
%\documentclass[a4paper,10pt]{scrartcl}

\usepackage[utf8]{inputenc}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green]{hyperref}
\usepackage{CJK}
\usepackage{verbatim}


\title{雅思}
\author{Marvin}
\date{}

\pdfinfo{%
  /Title    ()
  /Author   ()
  /Creator  ()
  /Producer ()
  /Subject  ()
  /Keywords ()
}

\begin{document}

\begin{CJK*}{UTF8}{gkai}

\newpage
\section{List 1}
\begin{itemize}
\item abate   降价，减轻\\
\hspace{1cm}After the closedown of the airport,noise pollution abated.
\item abhorrent 可恶的，可恨的\\
\hspace{1cm}As far as I am concerned,the practice of killing rare wild animals for food and money is utterly abhorrent and should be punished by law.
\item abide 停留，忍受\\
\hspace{1cm}Anyone can abide by what he or she said,but it doesn't mean all of them are correct.
\item abode 家\\
\hspace{1cm}I do not dare to linger in that gloom-hidden abode.
\item abound  充满\\
\hspace{1cm}The mountain streems abound with fish.
\item absurd 荒谬的，荒唐的\\
\hspace{1cm}Wearing a swimming suit during a snowstorm is absurd.
\item acclaim  欢呼，喝彩\\
\hspace{1cm}win worldwide acclaim
\item acclimatise 水土不服，适应新环境\\
\hspace{1cm}After a couple of days to acclimatise yourself,you'll start the trek on day three walking through the enormous Katiba Forest which will take the whole of the day.
\item accredit 信任\\
\hspace{1cm}Scolded by the boss for many times,the young man was accredited as department manager,which is a suddenness for everybody.
\item acoustic 原声的\\
\hspace{1cm}In the houses near the highway special acoustic seals should be fitted to the doors to reduce noise.
\item adjunct 附件\\
\hspace{1cm}Responsible ,compassionate sex should be an adjunct to the process of coupling,not the prime reason for doing so.
\end{itemize}


\newpage
\section{List 2}
\begin{itemize}
\item advent 出现，到来\\
\hspace{1cm} Sea ports have been transformed by the advent of powered vessels,whose size and draught have increased.
\item aeration 通风\\
\hspace{1cm}The tunnels abandoned by the bettles provide excellent aeration and water channels for root systems of plants.
\item aerobics 有氧运动\\
\hspace{1cm}This room is used mainly for badminton and aerobics.
\item aeronautics 航空学\\
\hspace{1cm}The Aeronautics Building is on the left side of the university campus.
\item afflict 折磨\\
\hspace{1cm}Financial difficulties afficted the Smiths.
\item ailment 疾病\\
\hspace{1cm}New medical technology will cure more ailments that afflict humanity.
\item alight 飞落\\
\hspace{1cm}The earliest peoples probably stored fire by keeping slow burning logs alight or by carrying charcoal in pots.
\item allergic 过敏\\
\hspace{1cm}an allergic reaction
\item allure 诱惑\\
\hspace{1cm}According to the statistics,the allure of the big city has weakened because of high housing prices.
\item alluvial 淤泥\\
\hspace{1cm}The seabed here consisted of alluvial sit and mud deposits.
\item almond 杏仁\\
\hspace{1cm}Mary prefers almonds to peanuts.
\item amorphous 无组织的，无固定形状 \\
\hspace{1cm}The Swedish chemist called Pasch discovered amorphous phosphorus.
\end{itemize}


\newpage
\section{List 3}
\begin{itemize}
\item anatomy 解剖\\
\hspace{1cm}Leon devoted his life to studying the human anatomy.
\item anthropologist 人类学家\\
\hspace{1cm}The lecturer is an anthropologist.
\item antique 古老的\\
\hspace{1cm}There is an antique mahogany desk exhibited in the corner.
\item antiseptic 抗菌的\\
\hspace{1cm}In old times,the bodies of most of emperors were dealt with antiseptic for lasting for ever.
\item appliance 用具\\
\hspace{1cm}On Wednesdays,I repair electrical appliances free of charge..
\item appraisal 评估\\
\hspace{1cm}Susan's appraisal of the writer's work was favorable.
\item aquarium 玻璃缸\\
\hspace{1cm}We are going to take the kids to the new aquarium this weekend.
\item arboreal 树木的\\
\hspace{1cm}Koala is an arboreal animal.
\item aridity 干旱\\
\hspace{1cm}The most challenging natural problem of Australia is aridity.
\item arousal 唤起\\
\hspace{1cm}The physiological arousal declined quickly to the same levels as those of the control subjects.
\item artery 动脉，干道\\
\hspace{1cm}The patient underwent an operation to unblock his coronary artery.
\end{itemize}


\newpage
\section{List 4}
\begin{itemize}
\item assemble 集合，装配\\ 
\hspace{1cm}Allcomponents were assembled in the front workshop.
\item asset 财产，优点\\
\hspace{1cm}Organizations should recognize that their employees are a significant part of their financial assets.
\item assimilate 吸收，同化\\
\hspace{1cm}We assimilate some kinds of food more easily than others.
\item astound 震惊\\
\hspace{1cm}The eruption in May 1980 of Mount St. Helens ,Washington State,astounded the world with its violence.
\item astrology  占星术\\
\hspace{1cm}
\item asymmetry 不对称\\
\hspace{1cm}Asymmetry is a common feature of the human body.
\item audacious 大胆的\\
\hspace{1cm}The audacious proposal was quickly denied by the committee.
\item audit 审计，查帐\\
\hspace{1cm}It is a busy time for him that he has to audit the accounts of that company.
\item autocratic 独裁的，专制的\\
\hspace{1cm}
\item autonomy 自治权\\
\hspace{1cm}
\item avalanche 雪崩\\
\hspace{1cm}An earthquake triggered an avalanche.
\end{itemize}

\newpage
\section{List 5}
\begin{itemize}
\item badge 标记，象征 \\
\hspace{1cm}Are there any marks of badges on your briefcase that make it stand out?
\item baffle 使困惑，难倒\\
\hspace{1cm}All of us are baffled why she didn't give us the notice.
\item barbaric 野蛮的，粗鲁的\\
\hspace{1cm}The animal protectors consider the idea of killing wild animals for pleasure extremely barbaric.
\item baron 贵族，男爵\\
\hspace{1cm}
\item barrage 弹幕射击，火力网\\
\hspace{1cm}The army has laid down a barrage.
\item bead 水滴，珠子\\
\hspace{1cm}Don't trifle that string of purple beads which values more than five million dollars.
\item begrimed 污秽的\\
\hspace{1cm}In recent years,more and more begrimed articles and videos have spread by means of Internet and mobile phones.
\item begrudge 嫉妒，对...不满\\
\hspace{1cm}The rich ,who saw their income slashed,did begrudge sharing their gains with the poor.
\item bereave 使丧失，剥夺\\
\hspace{1cm}Nobody can bereave wild animals and plants of their survival on the blue planet where we live together.
\item bilateral 双边的\\
\hspace{1cm}The two countries worked out a bilateral agreement.
\item bistro 小酒馆\\
\hspace{1cm}The Geneva Bistro is always a popular place in this area.
\end{itemize}

\newpage
\section{List 6}
\begin{itemize}
\item bleak 寒冷的，阴沉的
\hspace{1cm}
\item bolster 支持，改善
\hspace{1cm}
\item boulder 大石头
\hspace{1cm}
\item breeze 微风
\hspace{1cm}
\item brew 冲泡，酝酿
\hspace{1cm}
\item bronchitis 支气管炎
\hspace{1cm}
\item browse 吃嫩叶或草，浏览
\hspace{1cm}
\item brunt 冲击
\hspace{1cm}
\item brutal 残忍的
\hspace{1cm}
\item bulge 膨胀
\hspace{1cm}
\item bully 侍强凌弱，欺负
\hspace{1cm}
\item bump 碰撞
\hspace{1cm}
\item bungalow 平房
\hspace{1cm}
\item burgeon 迅速成长
\hspace{1cm}
\end{itemize}


\newpage
\section{List 7}
\begin{itemize}
\item burglar 窃贼 
\hspace{1cm}
\item burrow 挖掘，地洞
\hspace{1cm}
\item calf 牛犊，幼仔
\hspace{1cm}
\item calibrate 标准，划分
\hspace{1cm}
\item calibre 质量，才干，能力
\hspace{1cm}
\item camouflage 伪装
\hspace{1cm}
\item canteen 餐厅
\hspace{1cm}
\item cardiovascular 心血管的
\hspace{1cm}
\item carousel 传送带
\hspace{1cm}
\item cascade 瀑布
\hspace{1cm}
\item caustic 腐蚀性的，挖苦的
\hspace{1cm}
\item cavort 欢呼
\hspace{1cm}
\item censure 指责，谴责 
\hspace{1cm}
\item ceramic 陶器的
\hspace{1cm}
\item cervical 子宫的，颈部的
\hspace{1cm}
\item chamber 室，洞穴
\hspace{1cm}
\item 
\end{itemize}

\newpage
\section{List 8}
\begin{itemize}
\item chancellor 大臣 
\hspace{1cm}
\item chapel 小教堂
\hspace{1cm}
\item charcoal 炭
\hspace{1cm}
\item chink 裂缝
\hspace{1cm}
\item cholesterol 胆固醇
\hspace{1cm}
\item chronic 慢性的，积习难改的
\hspace{1cm}
\item churn 搅乳器
\hspace{1cm}
\item clot 凝块
\hspace{1cm}
\item clumsy 笨重的
\hspace{1cm}
\item clutch 离合器 控制，抓紧
\hspace{1cm}
\item coffer 保险箱
\hspace{1cm}
\item 
\hspace{1cm}
\item 
\hspace{1cm}
\item 
\hspace{1cm}
\item 
\hspace{1cm}
\item 
\hspace{1cm}
\end{itemize}

\newpage
\section{List 9}
\begin{itemize}
\item colossal 庞大的，巨大的
\hspace{1cm}
\item combustion 联合体
\hspace{1cm}
\item commiserate 怜悯，同情
\hspace{1cm}
\item commute 上下班往返，交换，抵偿
\hspace{1cm}
\item compatriot 同胞
\hspace{1cm}
\item compendium 简要，概略
\hspace{1cm}
\item compromise 折中
\hspace{1cm}
\item compulsively 强制地
\hspace{1cm}
\end{itemize}

\newpage
\section{List 10}
\begin{itemize}
\item concession 让步，迁就 
\hspace{1cm}
\item condensation 浓缩
\hspace{1cm}
\item condone 宽恕，赦免
\hspace{1cm}
\item conduce 有益于
\hspace{1cm}
\item conform 遵守，服从，适应，一致
\hspace{1cm}
\item consecutive 连续不断的
\hspace{1cm}
\item consignment 交付，投递
\hspace{1cm}
\item consortium 集团，财团
\hspace{1cm}
\item constituent 成分，要素，选民，组成
\hspace{1cm}
\end{itemize}

\newpage
\section{List 11}
\begin{itemize}
\item contaminant 污染物 
\hspace{1cm}
\item contemplate 思量，沉思，预期
\hspace{1cm}
\item contempt 轻视，不尊重
\hspace{1cm}
\item continent 大陆，洲
\hspace{1cm}
\item contingency 偶然性
\hspace{1cm}
\item contrived 不自然的，人为的
\hspace{1cm}
\item convection 传送，对流
\hspace{1cm}
\item coral 珊瑚虫，红色的
\hspace{1cm}
\item cord 线，带
\hspace{1cm}
\item cork 软木塞
\hspace{1cm}
\item corporal 肉体的，身体的，下士
\hspace{1cm}
\item corps 军团
\hspace{1cm}
\item corpus 文献
\hspace{1cm}
\item corrode 腐蚀
\hspace{1cm}
\item cosmopolitan 世界性的，全球的
\hspace{1cm}
\item cosset 溺爱
\hspace{1cm}
\item costume 戏装
\hspace{1cm}
\item counter 柜台，相反地
\hspace{1cm}
\item counterpart 配对物，副本
\hspace{1cm}
\item coupon 优惠券，票证，订货单
\hspace{1cm}
\end{itemize}

\newpage
\section{List 12}
\begin{itemize}
\item crank 曲柄，转动某物 
\hspace{1cm}
\item crater 火山口，坑
\hspace{1cm}
\item credential 证明，证件
\hspace{1cm}
\item creep 爬，悄悄移动
\hspace{1cm}
\item crescent 新月
\hspace{1cm}
\item cricket 板球，蟋蟀
\hspace{1cm}
\item crisp 脆的
\hspace{1cm}
\item crockery 陶器
\hspace{1cm}
\item crude 粗鲁的，天然的
\hspace{1cm}
\item cruise 航游，巡航
\hspace{1cm}
\item crusade 十字军，斗争
\hspace{1cm}
\item culminate 结束
\hspace{1cm}
\item cultivate 种植
\hspace{1cm}
\item curative 有疗效的
\hspace{1cm}
\item curb 抑制，约束
\hspace{1cm}
\item curry 咖喱饭
\hspace{1cm}
\item curtail 削减，剥夺
\hspace{1cm}
\item daunt 使气馁
\hspace{1cm}
\item dearth 缺乏，短缺
\hspace{1cm}
\end{itemize}



\newpage
\section{List 13}
\begin{itemize}
\item debris 残骸，碎屑 
\hspace{1cm}
\item decapitate 斩首
\hspace{1cm}
\item decay 腐烂
\hspace{1cm}
\item decibel 分贝
\hspace{1cm}
\item decipher 破译
\hspace{1cm}
\item decrepit 破旧的，衰老的
\hspace{1cm}
\item deem 认为
\hspace{1cm}
\item deficit 赤字
\hspace{1cm}
\item deflect 偏斜
\hspace{1cm}
\item delinquency 失职
\hspace{1cm}
\item demerit 过失
\hspace{1cm}
\item demographic 人口学
\hspace{1cm}
\item demolish 破坏，拆除
\hspace{1cm}
\item denomination 命名
\hspace{1cm}
\item depict 描绘
\hspace{1cm}
\item deplete 消耗
\hspace{1cm}
\item deputy 代表
\hspace{1cm}
\item derelict 衰退的，破败的
\hspace{1cm}
\end{itemize}

\newpage
\section{List 14}
\begin{itemize}
\item despoil 抢夺
\hspace{1cm}
\item detergent 净化的
\hspace{1cm}
\item deteriorate 变坏，恶化
\hspace{1cm}
\item detrimental 不利的
\hspace{1cm}
\item devastate 破坏
\hspace{1cm}
\item deviance 异常
\hspace{1cm}
\item diesel 柴油
\hspace{1cm}
\item dietary 饮食的
\hspace{1cm}
\item discipline 训练
\hspace{1cm}
\item discrepancy 不同，矛盾
\hspace{1cm}
\item disdain 鄙视，蔑视
\hspace{1cm}
\end{itemize}

\newpage
\section{List 15}
\begin{itemize}
\item 
\hspace{1cm}
\item 
\hspace{1cm}
\item 
\hspace{1cm}
\item 
\hspace{1cm}
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\end{itemize}

\newpage
\section{List 16}
\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\end{itemize}

\newpage
\section{List 17}
\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\end{itemize}

\newpage
\section{List 18}
\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\end{itemize}

\newpage
\section{List 19}
\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\end{itemize}

\newpage
\section{List 20}
\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\end{itemize}

\newpage
\section{List 21}
\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\end{itemize}

\newpage
\section{List 22}
\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\end{itemize}

\newpage
\section{List 23}
\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\end{itemize}

\newpage
\section{List 24}
\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\end{itemize}

\newpage
\section{List 25}
\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\end{itemize}

\newpage
\section{List 26}
\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\end{itemize}

\newpage
\section{List 27}
\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\end{itemize}

\newpage
\section{List 28}
\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\end{itemize}

\newpage
\section{List 29}
\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\end{itemize}

\newpage
\section{List 30}
\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\end{itemize}

\newpage
\section{List 31}
\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\end{itemize}

\newpage
\section{List 32}
\begin{itemize}
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\item 
\end{itemize}
\end{CJK*}

\end{document}
